---
title: ""
output: 
  pdf_document:
  fig_caption: true
fontfamily: mathpazo
fontsize: 11pt
highlight: tango
number_sections: yes
latex_engine: pdflatex
keep_tex: true
classoption: portrait
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=1.6cm"
params:
  invc_client: NA
  invc_table: NA
  due_date: NA
  invoice_no: NA
  client_in: NA
  company_mine: NA
  address_mine_1: NA
  address_mine_2: NA
  address_mine_3: NA
  address_mine_4: NA
  company_client: NA
  address_client_1: NA
  address_client_2: NA
  address_client_3: NA
  address_client_4: NA
  account_holder: NA
  account_number: NA
  account_bank: NA
  contact: NA
  email: NA
  phone: NA
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \usepackage{titling}
  - \pretitle{\begin{flushleft}}
  - \posttitle{\end{flushleft}}
  - \usepackage{fancyhdr}
---

\begin{flushright}
\includegraphics[width=7cm]{/home/callum28/nexus/apps/pckgs/invoicer/invoicer/inst/app/mrkdn/nexus_logo.png}
\end{flushright}


```{r echo=FALSE}

pacman::p_load(
  knitr
  , rmarkdown
  , dplyr
  # , grid
  # , gridExtra
  # , tidyr
  # , tibble
  # , stringr
  # , lubridate
  # , purrr
  # , readr
  # , skimr
  # , ggplot2
  # , forcats
  # , packcircles
  # , lubridate
  # , tsibble
  # , glue
  # , tidyquant
  # , viridis
  # , plotly
)


```


```{r dev, echo=FALSE}

# invc_client      <- readr::read_rds('invc_client_rctv.rds')
# due_date         <- 'Payable on Receipt'
# invoice_no       <- 'inv_no'
# client_in        <-  'client_in'
# company_mine     <- 'My Company Name'
# address_mine_1   <- '39 Toytown Street'
# address_mine_2   <- 'Capetown'
# address_mine_3   <- 'South Africa'
# address_mine_4   <- '7782'
# company_client   <- 'myclient'
# address_client_1 <- '71 Goofy Street'
# address_client_2 <- 'Capetown'
# address_client_3 <- 'South Africa'
# address_client_4 <- '7977'
# account_holder   <- 'Mr John Johnson'
# account_number   <- 62199999999
# account_bank     <- 'Big Bank Company'
# contact          <- 'John Johnson'
# email            <- 'johnjohnson999@gmail.com'
# phone            <- '0799999999'




```



```{r}


```


```{r,  echo=FALSE, results='asis'}

cat('**INVOICE**')

```


```{r prod, echo=FALSE}

invc_client <- params$invc_client
invc_table  <- params$invc_table 

# invoice_table <- readr::read_rds('invoice_table_rctv.rds')


due_date         <- params$due_date
invoice_no       <- params$invoice_no
client_in        <- params$client_in
company_mine     <- params$company_mine
address_mine_1   <- params$address_mine_1
address_mine_2   <- params$address_mine_2
address_mine_3   <- params$address_mine_3
address_mine_4   <- params$address_mine_4
company_client   <- params$company_client
address_client_1 <- params$address_client_1
address_client_2 <- params$address_client_2
address_client_3 <- params$address_client_3
address_client_4 <- params$address_client_4
account_holder   <- params$account_holder
account_number   <- params$account_number
account_bank     <- params$account_bank
contact          <- params$contact
email            <- params$email
phone            <- params$phone


```


```{r, echo=FALSE}

x_table <- tibble::tibble(
  item = c('Invoice Date'
           , 'Invoice No'
           , 'Client', 'Due Date'
  )
  , value = c(
    as.character(Sys.Date())
    , invoice_no
    , client_in, due_date
  )
)
# %>%
#   kable(
#     align= c('r','l')
#     , col.names = NULL
#     )

# x_table

```

```{r, results='asis', echo=FALSE}

cat(glue::glue('Invoice Date: {x_table$item[1]}'))

```

```{r, results='asis', echo=FALSE}

cat(glue::glue('Invoice No: {x_table$item[1]}'))

```

```{r, results='asis', echo=FALSE}

cat(glue::glue('Account: {x_table$item[1]}'))

```

```{r, results='asis', echo=FALSE}

cat(glue::glue('Due Date: {x_table$item[1]}'))

```


\begin{minipage}[t]{0.5\textwidth}
.\newline
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\begin{flushright}


```{r, results='asis', echo=FALSE}



```


```{r, results='asis', echo=FALSE}
cat(company_mine)
```

```{r, results='asis', echo=FALSE}
cat(address_mine_1)
```

```{r, results='asis', echo=FALSE}
cat(address_mine_2)
```

```{r, results='asis', echo=FALSE}
cat(address_mine_3)
```

```{r, results='asis', echo=FALSE}
cat(address_mine_4)
```


\end{flushright}
\end{minipage}

```{r, echo=FALSE}



```

**Bill to:**

\begin{minipage}[t]{0.5\textwidth}

```{r, results='asis', echo=FALSE}
cat(company_client)
```

```{r, results='asis', echo=FALSE}
cat(address_client_1)
```

```{r, results='asis', echo=FALSE}
cat(address_client_2)
```

```{r, results='asis', echo=FALSE}
cat(address_client_3)
```

```{r, results='asis', echo=FALSE}
cat(address_client_4)
```

\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\end{minipage}

****

```{r}

```


```{r, echo=FALSE, message=FALSE}

invc_table %>%
  # bind_rows(tibble::tibble(
  #   role = 'TOTAL'
  #   , rate = ''
  #   , currency = ''
  #   , hours = ''
  #   , sub_total = sum(.$sub_total)
  # )) %>%
  kable()

```




```{r}

```


```{r,  echo=FALSE, results='asis'}

cat("\\ ")
cat("\\linebreak")
cat("\\linebreak")
cat("\\linebreak")
cat("\\linebreak")

```



```{r,  echo=FALSE, results='asis'}

cat('**Please make payment to: **')

```


```{r,  echo=FALSE, results='asis'}

cat(glue::glue('Account Holder :  {account_holder}'))

```


```{r,  echo=FALSE, results='asis'}

cat(glue::glue('Account Number :  {account_number}'))

```


```{r,  echo=FALSE, results='asis'}

cat(glue::glue('Bank :  {account_bank}'))

```

****



\bcenter

```{r,  echo=FALSE, results='asis'}

cat(glue::glue('If you have any questions about this invoice, please contact {contact}.'))

```

```{r,  echo=FALSE, results='asis'}

cat(glue::glue('Email: {email}.'))
```

```{r,  echo=FALSE, results='asis'}

cat(glue::glue('Cell : {phone}.'))
```



\ecenter

****

\clearpage
\newpage

```{r, echo=FALSE}

invc_client 
# %>%
#   select(role, date, start, end_time, hours) %>%
#   kable()

```

\bcenter

Thank you for your business!

\ecenter
